Cradles of the first stars: self-shielding, halo masses, and multiplicity

### 2019-08-12 referee.tex
minor change

We chose this critical H$_2$ fraction to match with the values found in previous work (e.g. Yoshida et al. 2007; Omukai et al. 2010) at the density threshold of $10^6 \cubecm$.  It is a number fraction.  We have added a note in Section 2.2.1 to reflect this detail.

@@

The occurrence of BH formation and no metal enrichment depends on the chosen Pop III IMF, and we have addressed in an earlier answer and made a note in Section 2.2.1.

>>>>

We chose this critical H$_2$ fraction to match with the values found in previous work (e.g. Yoshida et al. 2007; Omukai et al. 2010) at the density threshold of $10^6 \cubecm$.  It is a number fraction.  We have added to Section 2.2.1 to reflect this detail.

@@

The occurrence of BH formation and no metal enrichment depends on the chosen Pop III IMF, and we have addressed in an earlier answer and noted this fraction in the discussion.
